Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-02-12 Paper.tex
9.4.3. Jump Destination Validity - be explicit about validation
The sentence "must appear within the explicitly defined portion of the code"
leads the reader to think that only executable code is checked for JUMPDEST validity.
In practice, all clients validate jump destinations prior to execution.

All such positions must be on valid instruction boundaries, rather than sitting in the data portion of {\small PUSH} operations and must appear within the explicitly defined portion of the code (rather than in the implicitly defined \hyperlink{stop}{{\small STOP}} operations that trail it).

>>>>

All such positions must be on valid instruction boundaries, rather than sitting in the data portion of {\small PUSH} operations and must appear within the explicitly defined portion of the code (rather than in the implicitly defined \hyperlink{stop}{{\small STOP}} operations that trail it), where code denotes any executable code or data (non-reachable by Program Counter) between {\small PUSH} operations. Jump destinations must be validated prior to execution.
